How to Learn Useful Changes to Software Projects\\(to Reduce Runtimes and Software Defects)

### 2015-08-23 Manuscript.tex
Updates from ShareLaTeX

Our answer is ``yess'', if those changes select for the {\em region of competency} of the predictor. When we assess
any data miner, there are two ``clouds'' of data:
\bi
\item One cloud is the space of training examples.
\item Another cloud is the space of test examples.
\ei
We should mistrust a model learned from data mining if the test examples  too far removed from the training data; i.e. if
these two clouds are too far apart. To test for ``too far'', we can run a data mining experiment to test how well
a model learned from the training data applies to the test data. Such experiments return some performance value, from
which we can say that if ever any new data falls into the combined region of the training+test cloud, then we should expect
at least that level of performance.

A corollary of the above is that if we are changing examples, and making predictions about those changed examples,
then:
\bi
\item Predictions about changes that move examples towards/away from the cloud of training data can be trusted more/less (respectively).
\item More specifically: predictions  about changes that  fall within the space of the training+test data, will be at least
as accurate as the 
\ei

>>>>

Our answer is ``yes'', if those changes select for the {\em region of competency} of the predictor. When we assess
any data miner, there are two ``clouds'' of data:
\bi
\item One cloud is the space of training examples.
\item Another cloud is the space of test examples.
\ei
We should mistrust a model learned from data mining if the test examples  too far removed from the training data; i.e. if
these two clouds are too far apart. To test for ``too far'', we can run a data mining experiment to test how well
a model learned from the training data applies to the test data. Such experiments return some performance value.
Given this, two things can be said about predictions on changed examples:
\bi
\item Predictions  about changes that  fall within the space of the training+test data, will be at least
as reliable as the performance value found in the data mining experiment.
\item More generally, predictions about changes that move examples towards/away from the cloud of training data can be trusted more/less (respectively).
\ei  
Accodringly, all the methods of this paper make {\em trust-increasing} recommendations. That is, they push change examples {\em towards} the
training examples.  To see how this works, 
 \fig{howxy} is from the {\em ivy} data
set, which is one of the Jureczk data set. It shows: (1)~the training examples, (2)~the test examples, and (3)~the
changed  examples displaced after applying one of our planning methods.
To generate that figure, we placed all of 1+2+3 into the same data set then computed the first
two  components (using PCA). Note that the  the   changed examples
cases  (shown in green)  fall closer to the training cases (shown in gray) than
the test cases (shown in red).  That is, if we believe
that the gray data is  suitable for assessing
the test cases (as indicated by the {\em ivy} results from \fig{j}), then it follows
that we believe even more in the predictions
generated from the displaced data).

This pattern of \fig{howxy} (where the displaced test cases are found closer to  the training cases than the test cases) has been observed in all the other data sets studied in this
paper. Hence,  we can assert that
predictors learned from these training data have some authority in the regions
used to generate the plans\footnote{If the reader is concerned that this 2d projection
losses important information, then they should note that two separate  studies~\cite{papa13,divya15}
have confirmed that building defect predictors from this 2d space are just as effective
as predictors learned using all the defect attributes of \fig{ck}.}.

\begin{figure}
\begin{center}\includegraphics[width=3in]{figs/2d.png}\end{center}
\caption{Training cases (in gray), test cases (in red) and 
test cases displaced by HOW (in green). Note how the green (displaced) cases are closer to the  training
date than the original test data
i.e. predictors trained on the training cases and
applied to the test cases should
work just as well, or better, on the displaced test cases.}\label{fig:howxy}
\end{figure}
%XXX end

That said, one thing to be said here
is that we {\em strongly} recommend that predictors are assessed prior to planning. That is
issue is explored further in the next section.
